Embedding Dimension of Polyhedral Losses

### 2020-01-31 colt-20/embed-dim.tex
Moved proof of prop 10 to appendix

\begin{definition}[Intersection graph]\label{def:intersection-graph}
  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \toto 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ is the relative interior of $\simplex$.
  %(distributions with full support).
\end{definition}
\begin{proposition} \label{prop:orderable-iff-path}
  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
\end{proposition}
\begin{proof}
  $(\implies)$
  The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
  If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace (this follows because the level sets form a power diagram, e.g.~\cite{lambert2009eliciting}).
  This yields a path for the intersection graph.

@@

\section{$1$-dimensional characterization omitted proofs}

>>>>

\begin{definition}[Intersection graph]\label{def:intersection-graph}
  Given a discrete loss $\ell$ and associated finite property $\gamma: \simplex \toto 2^{\R}$ elicited by $\ell$, the \emph{intersection graph} has vertices $\R$ with an edge $(r,r')$ if $\gamma_r \cap \gamma_{r'} \cap \relint(\simplex) \neq \emptyset$, where $\relint(\simplex)$ is the relative interior of $\simplex$.
  %(distributions with full support).
\end{definition}

If one can visualize the level sets of a property, constructing the intersection graph yields an intuitive way to conceptualize orderability by the Proposition below, proved in Appendix~\ref{app:1-dim}.

\begin{proposition} \label{prop:orderable-iff-path}
  A finite property $\gamma$ is \emph{orderable} if and only if its intersection graph is a path, i.e. a connected graph where every vertex has either one or two neighbors.
\end{proposition}

@@

\section{$1$-dimensional characterization omitted proofs}\label{app:1-dim}

\begin{proof}[Proof of Proposition~\ref{prop:orderable-iff-path}]
	$(\implies)$
	The intersection graph is constructed by adding an edge for each halfspace, which connects only two nodes.
	If three level sets intersected on $\relint(\simplex)$, then the level boundary for any two would not be a halfspace (this follows because the level sets form a power diagram, e.g.~\cite{lambert2009eliciting}).
	This yields a path for the intersection graph.
